BivData Setup

### 2020-02-14 src/BivData_Setup.Rmd
re-ran setup, rdata wasn't loading, clean up todos

declare the Strain specific BivData_DFs  (for convinice)

check the numbers of bivalents with a SC length, but no hand.foci.count

@@

#save Rdata
save.image("~./MLH1repo/data/CleanBivData_12.2.20.RData")
#save.image("data/BivData_4_PCA.RData")

>>>>

@@

#save Rdata
save.image("~./MLH1repo/data/CleanBivData_13.2.20.RData")
#save.image("data/BivData_4_PCA.RData")
